Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward

### 2022-06-16 analysis/paper/paper.Rmd
Wordsmithing and spelling corrections

We fitted Bayesian logistic mixed models (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000 and thinning of 1) using the `cumulative(link = "probit")` family function for ordinal data using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021].
Priors were selected to be weakly informative and deemed suitable through using `pp_check()` to examine the predictions based on priors only (using the parameter `sample_prior = only` in `brm()`).
Priors over all parameters were set as: normal (mean = 0.00, SD = 1.0) distributions for both fixed parameters and random intercepts.

The models' were structured as follows to predict two responses, computational methods and data availability.
To predict the responses with publishing journal (abbreviation was used throughout) the formula took the form: response ~ abbreviation and the models included assignee and year as random effects (formula: list(~1 | assignee, ~1 | year)).
To predict the response with year were predicted as (formula: response ~ year) and the models included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
To predict the responses with IF_5year the formula took the form response ~ IF_5year and included assignee as random effect (formula: ~1 | assignee) without journal as a random effect to mitigate correlation between impact factor and the journal of publication.

>>>>

We fitted Bayesian logistic mixed models (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000 and thinning of 1) using cumulative family function for ordinal data using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021].
The cumulative family allows for the probability of a given value is the probability of that value or any smaller value.
Priors were selected to be weakly informative and deemed suitable through using `pp_check()` to examine the the models' predictions based on priors only (using the parameter `sample_prior = only` in `brm()`).
Priors over all parameters were set as: normal (mean = 0.00, SD = 1.0) distributions for both fixed parameters and random effects.

The models' were structured as follows to predict two responses, the availability of computational methods and data that were created or collected for the manuscript.
To predict the responses with publishing journal (abbreviation was used throughout) the formula took the form: response ~ abbreviation and the models included assignee and year as random effects (formula: list(~1 | assignee, ~1 | year)).
To predict the response with year were predicted as (formula: response ~ year) and the models included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
To predict the responses with IF_5year the formula took the form response ~ IF_5year and included assignee as random effect (formula: ~1 | assignee) without journal as a random effect to mitigate correlation between impact factor and the journal of publication.
